---
title: "BTC_Prediction"
author: "Karin Chang 20750481"
date: "2022-11-26"
output: html_document
---

```{r setup, include=FALSE}
library(quantmod)
library(xts)
library(fUnitRoots)
library(forecast)
library(tseries)
library(TSA)
library(FinTS)
library(fGarch)
library(rugarch)
```

## Get Data

```{r}

#portfolio = c("BTC-USD","ETH-USD","LTC-USD","XRP-USD","ADA-USD")
portfolio = c("BTC-USD")
getSymbols(portfolio, src="yahoo", from="2000-01-01")
tail(`BTC-USD`)

chartSeries(`BTC-USD`)
barChart(`BTC-USD`,theme='white.mono',bar.type='hlc')
# 
# chartSeries(`ETH-USD`)
# barChart(`BTC-USD`,theme='white.mono',bar.type='hlc')
# 
# chartSeries(`LTC-USD`)
# barChart(`BTC-USD`,theme='white.mono',bar.type='hlc')
# 
# chartSeries(`XRP-USD`)
# barChart(`BTC-USD`,theme='white.mono',bar.type='hlc')
# 
# chartSeries(`ADA-USD`)
# barChart(`BTC-USD`,theme='white.mono',bar.type='hlc')

```

## Prepare Data into different periodicity

```{r}
btc_daily <- to.period(`BTC-USD`, "days")
attr(btc_daily, 'frequency') <- 7
periodicity(btc_daily)

btc_weekly <- to.period(`BTC-USD`, "weeks")
attr(btc_weekly, 'frequency') <- 365.25/7
periodicity(btc_weekly)

btc_monthly <- to.period(`BTC-USD`, "months")
attr(btc_monthly, 'frequency') <- 12
periodicity(btc_monthly)

btc_logrtn_daily <- Delt(Cl(`BTC-USD`),type='log') # same as diff(log(`BTC-USD`[, 4]))
btc_logrtn_weekly <- Delt(Cl(btc_weekly),type='log')
btc_logrtn_monthly <- Delt(Cl(btc_monthly),type='log')
```


## Data Exploration on Daily Log Return

```{r}
chartSeries(
  btc_logrtn_daily, type="l", TA=NULL, 
  name="Daily Log Returns",
  theme="white", major.ticks="years", minor.ticks=FALSE)

x <- coredata(btc_logrtn_daily)
hist(x, main="Daily Log Returns", xlab="", ylab="")

qqnorm(x, main="Daily Log Returns")
qqline(x, col="red")

fBasics::basicStats(x)

tmp.1 <- density(x, na.rm=TRUE)
tmp.x <- seq(min(x, na.rm=TRUE), max(x, na.rm=TRUE), 
             length.out=100)
tmp.y <- dnorm(tmp.x, mean(x, na.rm=TRUE), 
               sd(x, na.rm=TRUE))
tmp.ra <- range(c(tmp.1$y, tmp.y), na.rm=TRUE)
plot(tmp.1, main="Daily Log Return", 
     ylim=tmp.ra)
lines(tmp.x, tmp.y, lwd=2, col="red")
legend("topleft", lwd=c(1,2), 
       col=c("black", "red"),
       legend=c("Kernel density Est.", 
                "Parametric normal density est."))

t.test(x)
tmp <- fBasics::basicStats(x)["Skewness", 1]; tmp
tmp/sqrt(6/length(x))

tmp <- fBasics::basicStats(x)["Kurtosis", 1]; tmp
tmp/sqrt(24/length(x))

fBasics::normalTest(x, method="jb")
```


## Data Exploration on Volatility of Daily Log Return

```{r}
library(PerformanceAnalytics)

chart.RollingPerformance(R = btc_logrtn_daily,
                         width = 30,
                         FUN = "sd.annualized",
                         scale = 365.25,
                         main = "Bitcoin's monthly rolling volatility")
```


## Decompose TimeSeries
```{r, include=FALSE}
decompose.xts <-
  function (x, type = c("additive", "multiplicative"), filter = NULL) 
  {
    dts <- decompose(as.ts(x), type, filter)
    dts$x <- .xts(dts$x, .index(x))
    dts$seasonal <- .xts(dts$seasonal, .index(x))
    dts$trend <- .xts(dts$trend, .index(x))
    dts$random <- .xts(dts$random, .index(x))
    
    with(dts,
         structure(list(x = x, seasonal = seasonal, trend = trend,
                        random = if (type == "additive") x - seasonal - trend else x/seasonal/trend, 
                        figure = figure, type = type), class = "decomposed.xts"))
  }

plot.decomposed.xts <-
  function(x, ...)
  {
    xx <- x$x
    if (is.null(xx))
      xx <- with(x,
                 if (type == "additive") random + trend + seasonal
                 else random * trend * seasonal)
    p <- cbind(observed = xx, trend = x$trend, seasonal = x$seasonal, random = x$random)
    plot(p, main = paste("Decomposition of", x$type, "time series"), multi.panel = 4,
         yaxis.same = FALSE, major.ticks = "years", grid.ticks.on = "years", ...)
  }
```


### Monthly Price

```{r}
#log transformation on monthly close price 
log_btc_monthly <-log(Cl(btc_monthly))
plot(log_btc_monthly)

# test H0 non-stationary 
adf.test(log_btc_monthly)

# test H0 white noise
Box.test(log_btc_monthly, lag=48, type="Ljung") 

# decompose component on log price
btc_tscomponents <- decompose(as.ts(log_btc_monthly))
plot(btc_tscomponents, col = "red")

dex <- decompose.xts(log_btc_monthly)
plot(dex)
```

### Weekly Price
```{r}
#log transformation on monthly close price 
log_btc_weekly <-log(Cl(btc_weekly))
plot(log_btc_weekly)

# test H0 non-stationary 
adf.test(log_btc_weekly)

# test H0 white noise
Box.test(log_btc_weekly, lag=48, type="Ljung") 

# decompose component on log price
btc_tscomponents <- decompose(as.ts(log_btc_weekly))
plot(btc_tscomponents, col = "red")

dex <- decompose.xts(log_btc_weekly)
plot(dex)
```

### Daily Price
```{r}
#log transformation on monthly close price 
log_btc_daily <-log(Cl(btc_daily))
plot(log_btc_daily)

# test H0 non-stationary 
adf.test(log_btc_daily)

# test H0 white noise
Box.test(log_btc_daily, lag=48, type="Ljung") 

# decompose component on log price
btc_tscomponents <- decompose(as.ts(log_btc_daily))
plot(btc_tscomponents, col = "red")

dex <- decompose.xts(log_btc_daily)
plot(dex)
```

## Test on WhiteNoise/Stationary/ARCH effect on log return series

### Daily Log Return
```{r}
diff1_log_btc_daily <- diff(log_btc_daily, differences=1) # same as btc_logrtn_daily
diff1_log_btc_daily <- na.omit(diff1_log_btc_daily)
plot(diff1_log_btc_daily, col = "red")
#plot(btc_logrtn_daily, col = "red")

# test non-stationary
adf.test(diff1_log_btc_daily)

# test white noise
Box.test(diff1_log_btc_daily, lag=60, type="Ljung") 

acf(ts(diff1_log_btc_daily), main='Daily Log Return', lag=60)
pacf(ts(diff1_log_btc_daily),main='Daily Log Return', lag=60) 

# test arch effect
acf(ts(diff1_log_btc_daily^2),60, col="red", main='Squared Daily Log Return')
Box.test(diff1_log_btc_daily^2,lag=60,type="Ljung")

atDaily=diff1_log_btc_daily-mean(diff1_log_btc_daily)
acf(ts(atDaily^2),60,col="red", main='Residual on Daily Log Return Mean equation')
Box.test(atDaily^2,lag=60,type="Ljung")

dex <- decompose.xts(diff1_log_btc_daily)
plot(dex)

```
daily log return series: stationary + white noise i.e. no serial correlations
squared series not white noise, indicating presence of ARCH effect

### Weekly Log Return
```{r}
diff1_log_btc_weekly <- diff(log_btc_weekly, differences=1) # same as btc_logrtn_weekly
diff1_log_btc_weekly <- na.omit(diff1_log_btc_weekly)
plot(diff1_log_btc_weekly, col = "red")
#plot(btc_logrtn_weekly, col = "red")

# test non-stationary
adf.test(diff1_log_btc_weekly)

# test white noise
Box.test(diff1_log_btc_weekly, lag=60, type="Ljung") 

acf(ts(diff1_log_btc_weekly), main='Weekly Log Return', lag=60)
pacf(ts(diff1_log_btc_weekly),main='Weekly Log Return', lag=60) 

# test arch effect
acf(ts(diff1_log_btc_weekly^2),60, col="red", main='Squared Weekly Log Return')
Box.test(diff1_log_btc_weekly^2,lag=60,type="Ljung")

atWeekly=diff1_log_btc_weekly-mean(diff1_log_btc_weekly)
acf(ts(atWeekly^2),60,col="red", main='Residual on Weekly Log Return Mean equation')
Box.test(atWeekly^2,lag=60,type="Ljung")

dex <- decompose.xts(diff1_log_btc_weekly)
plot(dex)
```
weekly log return series: stationary & white noise i.e. no serial correlations
squared series not white noise, indicating presence of ARCH effect

### Monthly Log Return
```{r}
diff1_log_btc_monthly <- diff(log_btc_monthly, differences=1) # same as btc_logrtn_monthly
diff1_log_btc_monthly <- na.omit(diff1_log_btc_monthly)
plot(diff1_log_btc_monthly, col = "red")
#plot(btc_logrtn_monthly, col = "red")

# test non-stationary
adf.test(diff1_log_btc_monthly)

# test white noise
Box.test(diff1_log_btc_monthly, lag=60, type="Ljung") 

acf(ts(diff1_log_btc_monthly), main='Monthly Log Return', lag=60)
pacf(ts(diff1_log_btc_monthly),main='Monthly Log Return', lag=60) 

# test arch effect
acf(ts(diff1_log_btc_monthly^2),60, col="red", main='Squared Monthly Log Return')
Box.test(diff1_log_btc_monthly^2,lag=60,type="Ljung")

atMonthly=diff1_log_btc_monthly-mean(diff1_log_btc_monthly)
acf(ts(atMonthly^2),60,col="red", main='Residual on Monthly Log Return Mean equation')
Box.test(atMonthly^2,lag=60,type="Ljung")

dex <- decompose.xts(diff1_log_btc_monthly)
plot(dex)
```

monthly log return series: stationary + serial correlations. 
squared series not white noise, indicating presence of ARCH effect


## Modelling

Train Test Split for Model Evaluation, later we will do 5-step ahead prediction
```{r}
h=5 # The forecasting horizon.

trainRow_Daily=nrow(diff1_log_btc_daily)-h
train_dailyR <- diff1_log_btc_daily[1:trainRow_Daily,]
test_dailyR <- diff1_log_btc_daily[-c(1:trainRow_Daily),]

# tail(train_dailyR)
# test_dailyR

trainRow_Weekly=nrow(diff1_log_btc_weekly)-h
train_weeklyR <- diff1_log_btc_weekly[1:trainRow_Weekly,]
test_weeklyR <- diff1_log_btc_weekly[-c(1:trainRow_Weekly),]

# tail(train_weeklyR)
# test_weeklyR

trainRow_Monthly=nrow(diff1_log_btc_monthly)-h
train_monthlyR <- diff1_log_btc_monthly[1:trainRow_Monthly,]
test_monthlyR <- diff1_log_btc_monthly[-c(1:trainRow_Monthly),]

# tail(train_monthlyR)
# test_monthlyR

```

### Daily

look for mean model if applicable
```{r}
mm_daily <- auto.arima(log_btc_daily)
mm_daily
```

coefficient insignificant, no mean model, look for volatility model


trying diff distribution model of residual with SGARCH, nig followed by std
yet none of them are adequate for daily return
```{r}
spec1=ugarchspec(variance.model=list(model="sGARCH",  garchOrder = c(1,1)),
                 mean.model=list(armaOrder=c(0,0),include.mean = TRUE),
                 distribution.model='norm')

mD1=ugarchfit(spec=spec1,data=train_dailyR)
show(mD1)
plot(mD1, which=9)

res_mD1=residuals(mD1)
Box.test(res_mD1,10,type="Ljung")
Box.test(res_mD1^2,10,type="Ljung")

spec2=ugarchspec(variance.model=list(model="sGARCH",  garchOrder = c(1,1)),
                 mean.model=list(armaOrder=c(0,0),include.mean = TRUE),
                 distribution.model='std')

mD2=ugarchfit(spec=spec2,data=train_dailyR)
mD2
plot(mD2, which=9)

res_mD2=residuals(mD2)
Box.test(res_mD2,10,type="Ljung")
Box.test(res_mD2^2,10,type="Ljung")

spec3=ugarchspec(variance.model=list(model="sGARCH",  garchOrder = c(1,1)),
                 mean.model=list(armaOrder=c(0,0),include.mean = TRUE),
                 distribution.model='ged'
                 )

mD3=ugarchfit(spec=spec3,data=train_dailyR)
mD3
plot(mD3, which=9)

res_mD3=residuals(mD3)
Box.test(res_mD3,10,type="Ljung")
Box.test(res_mD3^2,10,type="Ljung")

spec4=ugarchspec(variance.model=list(model="sGARCH",  garchOrder = c(1,1)),
                 mean.model=list(armaOrder=c(0,0),include.mean = TRUE),
                 distribution.model='nig'
                 )

mD4=ugarchfit(spec=spec4,data=train_dailyR)
mD4
plot(mD4, which=9)

res_mD4=residuals(mD4)
Box.test(res_mD4,10,type="Ljung")
Box.test(res_mD4^2,10,type="Ljung")
```



```{r}
mod1 <- garchFit(train_dailyR~1+garch(1,1), data=train_dailyR)
summary(mod1)

vola <- fGarch::volatility(mod1)
plot(ts(vola, start=start(train_dailyR), frequency=frequency(train_dailyR)), 
     xlab="year", ylab="volatility")
abline(h=sd(train_dailyR), col="green")
plot(mod1, which=3)

#garch - t
mod2 <- garchFit(~ 1 + garch(1,1), data=train_dailyR, 
                 cond.dist="std", trace=FALSE)
summary(mod2)
plot(mod2, which=13)


mod3 <- garchFit(~ 1 + garch(1,1), data=train_dailyR, 
                 cond.dist="sstd", trace=FALSE)
summary(mod3)

x.btc <- as.vector(time(train_dailyR))
vola1 <- fGarch::volatility(mod1)
vola2 <- fGarch::volatility(mod2)
vola3 <- fGarch::volatility(mod3)
matplot(x.btc, cbind(vola1, vola2, vola3),
        type="l",
        lty=1, col=c("green", "blue", "red"), 
        xlab="year", ylab="volatility")
legend('top', lty=1, col=c("green", "blue", "red"), 
       legend=c("Normal", "Student-t", "skewed t"))
```

```{r}
library(tibble)
p1 <- predict(mod1, n.ahead=h)[["standardDeviation"]]
p2 <- predict(mod2, n.ahead=h)[["standardDeviation"]]
p3 <- predict(mod3, n.ahead=h)[["standardDeviation"]]
pred.tab <- tibble(
  "n-head"=1:h,
  "normal"=p1,
  "student-t"=p2,
  "skewed t"=p3
)
knitr::kable(pred.tab, digits=4)
```

Tried eGARCH / iGARCH / gjrGARCH - all not adequate on daily return neither...

```{r}
spec1=ugarchspec(variance.model=list(model="eGARCH",  garchOrder = c(1,1)),
                 mean.model=list(armaOrder=c(0,0),include.mean = TRUE) )

mD1=ugarchfit(spec=spec1,data=train_dailyR)
show(mD1)
plot(mD1, which='all')

res_mD1=residuals(mD1,standardize=T)
Box.test(res_mD1,10,type="Ljung")
Box.test(res_mD1^2,10,type="Ljung")

spec2=ugarchspec(variance.model=list(model="iGARCH",  garchOrder = c(1,1)),
                 mean.model=list(armaOrder=c(0,0),include.mean = TRUE) )

mD2=ugarchfit(spec=spec2,data=train_dailyR)
mD2
plot(mD2, which='all')

res_mD2=residuals(mD2,standardize=T)
Box.test(res_mD2,10,type="Ljung")
Box.test(res_mD2^2,10,type="Ljung")

spec3=ugarchspec(variance.model=list(model="gjrGARCH",  garchOrder = c(1,1)),
                 mean.model=list(armaOrder=c(0,0),include.mean = TRUE) )

mD3=ugarchfit(spec=spec3,data=train_dailyR)
mD3
plot(mD3, which='all')

res_mD3=residuals(mD3,standardize=T)
Box.test(res_mD3,10,type="Ljung")
Box.test(res_mD3^2,10,type="Ljung")

```

### Weekly

look for mean model if applicable
```{r}
mm_weekly <- auto.arima(log_btc_weekly)
mm_weekly
```

coefficient insignificant, look for volatility model
```{r}

mod1 <- garchFit(~ 1 + garch(1,1), data=train_weeklyR)
summary(mod1)

vola <- fGarch::volatility(mod1)
plot(ts(vola, start=start(train_weeklyR), frequency=frequency(train_weeklyR)), 
     xlab="year", ylab="volatility")
abline(h=sd(train_weeklyR), col="green")
plot(mod1, which=3)

#garch - t
mod2 <- garchFit(~ 1 + garch(1,1), data=train_weeklyR, 
                 cond.dist="std", trace=FALSE)
summary(mod2)
plot(mod2, which=13)

mod3 <- garchFit(~ 1 + garch(1,1), data=train_weeklyR, 
                 cond.dist="sstd", trace=FALSE)
summary(mod3)
plot(mod3, which=13)

x.btc <- as.vector(time(train_weeklyR))
vola1 <- fGarch::volatility(mod1)
vola2 <- fGarch::volatility(mod2)
vola3 <- fGarch::volatility(mod3)
matplot(x.btc, cbind(vola1, vola2, vola3),
        type="l",
        lty=1, col=c("green", "blue", "red"), 
        xlab="year", ylab="volatility")
legend("top", lty=1, col=c("green", "blue", "red"), 
       legend=c("Normal", "Student-t", "skewed t"))

```

```{r}
spec0=ugarchspec(variance.model=list(model="sGARCH",  garchOrder = c(1,1)),
                 mean.model=list(armaOrder=c(0,0),include.mean = TRUE),
                 distribution.model = 'norm')

mW0=ugarchfit(spec=spec0,data=train_weeklyR)
show(mW0)
plot(mW0, which='all')

res_mW0=residuals(mW0,standardize=T)
Box.test(res_mW0,10,type="Ljung")
Box.test(res_mW0^2,10,type="Ljung")
```



Tried eGARCH / iGARCH / gjrGARCH - adequate for weekly return
gjrGARCH has the lowest AIC, then followed by sGARCH

```{r}
spec1=ugarchspec(variance.model=list(model="eGARCH",  garchOrder = c(1,1)),
                 mean.model=list(armaOrder=c(0,0),include.mean = TRUE) )

mW1=ugarchfit(spec=spec1,data=train_weeklyR)
show(mW1)
plot(mW1, which='all')

res_mW1=residuals(mW1,standardize=T)
Box.test(res_mW1,10,type="Ljung")
Box.test(res_mW1^2,10,type="Ljung")

spec2=ugarchspec(variance.model=list(model="iGARCH",  garchOrder = c(1,1)),
                 mean.model=list(armaOrder=c(0,0),include.mean = TRUE) )

mW2=ugarchfit(spec=spec2,data=train_weeklyR)
show(mW2)
plot(mW2, which='all')

res_mW2=residuals(mW2,standardize=T)
Box.test(res_mW2,10,type="Ljung")
Box.test(res_mW2^2,10,type="Ljung")

spec3=ugarchspec(variance.model=list(model="gjrGARCH",  garchOrder = c(1,1)),
                 mean.model=list(armaOrder=c(0,0),include.mean = TRUE) )

mW3=ugarchfit(spec=spec3,data=train_weeklyR)
show(mW3)
plot(mW3, which='all')

res_mW3=residuals(mW3,standardize=T)
Box.test(res_mW3,10,type="Ljung")
Box.test(res_mW3^2,10,type="Ljung")
```

```{r}
#plot(mW3@fit$var)
#plot(sigma(mW3))
```

Forecast with gjRGARCH(1,1) on weekly log return

5-step ahead prediction
```{r}
# estimate model excluding the out-of-sample

T <- nrow(diff1_log_btc_weekly)

out_of_sample <- round(T*.2)
dates_out_of_sample <- tail(index(diff1_log_btc_weekly), out_of_sample)
garch_spec <- ugarchspec(mean.model = list(armaOrder = c(0,0), include.mean = TRUE), 
                         variance.model = list(model = "gjrGARCH", garchOrder = c(1,1)))
garch_fit <- ugarchfit(spec = garch_spec, data = diff1_log_btc_weekly, out.sample = out_of_sample)
coef(garch_fit)

# forecast log-returns along the whole out-of-sample
garch_fore <- ugarchforecast(garch_fit, n.ahead = h, n.roll = out_of_sample-1)
forecast_log_returns <- xts(garch_fore@forecast$seriesFor[1, ], dates_out_of_sample)
forecast_volatility <- xts(garch_fore@forecast$sigmaFor[1, ], dates_out_of_sample)

# plot of log-returns
plot(cbind("fitted"   = fitted(garch_fit),
           "forecast" = forecast_log_returns,
           "original" = diff1_log_btc_weekly), 
     col = c("blue", "red", "black"), lwd = c(0.5, 0.5, 2),
     main = "Forecast of weekly BTC log-returns", legend.loc = "topleft")

# plot of volatility log-returns
plot(cbind("fitted volatility"   = sigma(garch_fit),
           "forecast volatility" = forecast_volatility,
           "log-returns"         = diff1_log_btc_weekly), 
     col = c("blue", "red", "black"), lwd = c(2, 2, 1),
     main = "Forecast of volatility of weekly BTC log-returns", legend.loc = "topleft")

```


rolling window comparison

```{r}
# model specification of an eGARCH(1,1)
spec <- garch_spec

# static fit and forecast
static_fit <- ugarchfit(spec = spec, data = diff1_log_btc_weekly, out.sample = out_of_sample)
static_fore_logreturns <- xts(ugarchforecast(garch_fit, n.ahead = h, n.roll = out_of_sample-1)@forecast$seriesFor[1, ],
                                 dates_out_of_sample)

# rolling fit and forecast
modelroll <- ugarchroll(spec = spec, data = diff1_log_btc_weekly, n.ahead = 1, 
                        forecast.length = out_of_sample, refit.every = 5, refit.window = "moving")
rolling_fore_logreturns <- xts(modelroll@forecast$density$Mu, dates_out_of_sample)

report(modelroll, type="VaR", VaR.alpha = 0.01, conf.level = 0.95)
report(modelroll, type="fpm")

# plot of forecast
plot(cbind("static forecast"  = static_fore_logreturns,
           "rolling forecast" = rolling_fore_logreturns),
     col = c("black", "red"), lwd = 2,
     main = "Forecast with gjrGARCH(1,1) model on Weekly Return", legend.loc = "topleft")

# plot of forecast error
error_logreturns <- cbind(diff1_log_btc_weekly - static_fore_logreturns,
                          diff1_log_btc_weekly - rolling_fore_logreturns)
names(error_logreturns) <- c("rolling forecast", "static forecast")
plot(error_logreturns, col = c("black", "red"), lwd = 2,
     main = "Forecast error with gjrGARCH(1,1) model on Weekly Return", legend.loc = "topleft")
```

log return to price

```{r}
# simulate one path
garch_spec <- ugarchspec(mean.model = list(armaOrder = c(0,0), include.mean = TRUE), 
                         variance.model = list(model = "gjrGARCH", garchOrder = c(1,1)),
                         fixed.pars = as.list(coef(garch_fit))
                                               )

T <- 36
path_garch <- ugarchpath(garch_spec, m.sim = 3, n.sim = T, rseed=1)

str(path_garch@path$seriesSim)
plot.zoo(fitted(path_garch))
plot.zoo(sigma(path_garch))

fOrigin <- tail(index(train_weeklyR), 1)
fOriginPrice <- as.numeric(btc_weekly[fOrigin]$`BTC-USD.Close`)

p<-fOriginPrice*apply(fitted(path_garch),2,'cumsum') + fOriginPrice
matplot(p, type='l', lwd=3, main = "BTC Weekly Closing Price from gjrGARCH model")

d <- seq(as.Date(fOrigin),by='weeks',length=T)
p.xts <- xts(p, order.by=d)
plot(cbind("forecast"=p.xts,
           "actual"=window(btc_weekly,start=fOrigin)$`BTC-USD.Close`
           ), 
     lwd=3, main = "BTC Weekly Closing Price from gjrGARCH model", legend.loc = "topleft")
```




### Monthly

look for mean model, recall significant spike at lag at 13 & 23
```{r}
acf <-acf(ts(diff1_log_btc_monthly), main='Monthly Log Return', lag=36)
acf

pacf <- pacf(ts(diff1_log_btc_monthly),main='Monthly Log Return', lag=36)
pacf

# try MA(13) and fix other coef to zero:
est = arima(diff1_log_btc_monthly,order=c(0,0,13),fixed=c(rep(0,12),NA,NA),seasonal=list(order=c(0,0,0),period=12))
est

jointTest= Box.test(est$residuals, lag=24, type="Ljung")
jointTest

pv=1-pchisq(jointTest$statistic[1],23) #Compute p-value using 8 degrees of freedom
names(pv) <- 'pv'
pv #0.5137

# try AR(13) and fix other coef to zero:
est = arima(diff1_log_btc_monthly,order=c(13,0,0),fixed=c(rep(0,12),NA,NA),seasonal=list(order=c(0,0,0),period=12))
est

jointTest= Box.test(est$residuals, lag=24, type="Ljung")
jointTest

pv=1-pchisq(jointTest$statistic[1],23) #Compute p-value using 8 degrees of freedom
names(pv) <- 'pv'
pv # 0.4895


# try ARMA(13,13) and fix other coef to zero: - NOT significant
est = arima(diff1_log_btc_monthly,order=c(13,0,13),
            fixed=c(rep(0,12),NA,rep(0,12),NA,NA),
            seasonal=list(order=c(0,0,0),period=12))
est

jointTest= Box.test(est$residuals, lag=24, type="Ljung")
jointTest

pv=1-pchisq(jointTest$statistic[1],23) #Compute p-value using 8 degrees of freedom
names(pv) <- 'pv'
pv #0.5111164

# look for arima model if applicable
mm_monthly <- auto.arima(log_btc_monthly)
mm_monthly

# conclusion: best model is the mean model.try MA(13) if insist on using ARMA as the mean model
```

volatility model for monthly return
sGARCH - adequate

```{r}
spec0=ugarchspec(variance.model=list(model="sGARCH",  garchOrder = c(1,1)),
                 mean.model=list(armaOrder=c(0,0),include.mean = TRUE) )

mM0=ugarchfit(spec=spec0,data=train_monthlyR)
show(mM0)
plot(mM0, which='all')

res_mM0=residuals(mM0,standardize=T)
Box.test(res_mM0,10,type="Ljung")
Box.test(res_mM0^2,10,type="Ljung")
```
eGARCH / iGARCH / gjrGARCH - all adequate for monthly return
compare AIC, eGARCH is the winner here. note the news impact curve is not symmetric compared with sGARCH

```{r}
spec1=ugarchspec(variance.model=list(model="eGARCH",  garchOrder = c(1,1)),
                 mean.model=list(armaOrder=c(0,0),include.mean = TRUE) )

mM1=ugarchfit(spec=spec1,data=train_monthlyR)
show(mM1)
plot(mM1, which='all')

res_mM1=residuals(mM1,standardize=T)
Box.test(res_mM1,10,type="Ljung")
Box.test(res_mM1^2,10,type="Ljung")

spec2=ugarchspec(variance.model=list(model="iGARCH",  garchOrder = c(1,1)),
                 mean.model=list(armaOrder=c(0,0),include.mean = TRUE) )

mM2=ugarchfit(spec=spec2,data=train_monthlyR)
mM2
plot(mM2, which='all')

res_mM2=residuals(mM2,standardize=T)
Box.test(res_mM2,10,type="Ljung")
Box.test(res_mM2^2,10,type="Ljung")

spec3=ugarchspec(variance.model=list(model="gjrGARCH",  garchOrder = c(1,1)),
                 mean.model=list(armaOrder=c(0,0),include.mean = TRUE) )

mM3=ugarchfit(spec=spec3,data=train_monthlyR)
mM3
plot(mM3, which='all')

res_mM3=residuals(mM3,standardize=T)
Box.test(res_mM3,10,type="Ljung")
Box.test(res_mM3^2,10,type="Ljung")
```

Forecast with EGARCH(1,1) on monthly log return

5-step ahead prediction
```{r}
# estimate model excluding the out-of-sample

T <- nrow(diff1_log_btc_monthly)

out_of_sample <- round(T*.2)
dates_out_of_sample <- tail(index(diff1_log_btc_monthly), out_of_sample)
garch_spec <- ugarchspec(mean.model = list(armaOrder = c(0,0), include.mean = TRUE), 
                         variance.model = list(model = "eGARCH", garchOrder = c(1,1)))
garch_fit <- ugarchfit(spec = garch_spec, data = diff1_log_btc_monthly, out.sample = out_of_sample)
coef(garch_fit)

# forecast log-returns along the whole out-of-sample
garch_fore <- ugarchforecast(garch_fit, n.ahead = h, n.roll = out_of_sample-1)
forecast_log_returns <- xts(garch_fore@forecast$seriesFor[1, ], dates_out_of_sample)
forecast_volatility <- xts(garch_fore@forecast$sigmaFor[1, ], dates_out_of_sample)

# plot of log-returns
plot(cbind("fitted"   = fitted(garch_fit),
           "forecast" = forecast_log_returns,
           "original" = diff1_log_btc_monthly), 
     col = c("blue", "red", "black"), lwd = c(0.5, 0.5, 2),
     main = "Forecast of monthly BTC log-returns", legend.loc = "topleft")

# plot of volatility log-returns
plot(cbind("fitted volatility"   = sigma(garch_fit),
           "forecast volatility" = forecast_volatility,
           "log-returns"         = diff1_log_btc_monthly), 
     col = c("blue", "red", "black"), lwd = c(2, 2, 1),
     main = "Forecast of volatility of monthly BTC log-returns", legend.loc = "topleft")


# trainRow_Monthly=nrow(diff1_log_btc_monthly)-h
# train_monthlyR <- diff1_log_btc_monthly[1:trainRow_Monthly,]
# test_monthlyR <- diff1_log_btc_monthly[-c(1:trainRow_Monthly),]
# 
# 
# sfinal <- mM1
# coef(mM1)
# 
# ugarchforecast(data=diff1_log_btc_monthly, fitORspec = mM1, n.ahead = h, n.roll = 1)


```

forecast error

```{r}
error_var <- rbind(
                   "eGARCH(1,1)" = c(var(diff1_log_btc_monthly - fitted(garch_fit)),
                                    var(diff1_log_btc_monthly - forecast_log_returns)))
colnames(error_var) <- c("in-sample", "out-of-sample")
print(error_var)
```
show some plots of the out-of-sample error

```{r}
error_logreturns <- cbind(diff1_log_btc_monthly - forecast_log_returns)
names(error_logreturns) <- c("eGARCH")
plot(error_logreturns, col = c("red"), lwd = c(1),
     main = "Out-of-sample error of static return forecast for different models", legend.loc = "bottomleft")
```

rolling window comparison
```{r}
# model specification of an eGARCH(1,1)
spec <- garch_spec

# static fit and forecast
static_fit <- ugarchfit(spec = spec, data = diff1_log_btc_monthly, out.sample = out_of_sample)
static_fore_logreturns <- xts(ugarchforecast(garch_fit, n.ahead = h, n.roll = out_of_sample-1)@forecast$seriesFor[1, ],
                                 dates_out_of_sample)

# rolling fit and forecast
modelroll <- ugarchroll(spec = spec, data = diff1_log_btc_monthly, n.ahead = 1, 
                        forecast.length = out_of_sample, refit.every = 5, refit.window = "moving")
rolling_fore_logreturns <- xts(modelroll@forecast$density$Mu, dates_out_of_sample)

report(modelroll, type="VaR", VaR.alpha = 0.01, conf.level = 0.95)
report(modelroll, type="fpm")

# plot of forecast
plot(cbind("static forecast"  = static_fore_logreturns,
           "rolling forecast" = rolling_fore_logreturns),
     col = c("black", "red"), lwd = 2,
     main = "Forecast with eGARCH(1,1) model on Monthly Return", legend.loc = "topleft")

# plot of forecast error
error_logreturns <- cbind(diff1_log_btc_monthly - static_fore_logreturns,
                          diff1_log_btc_monthly - rolling_fore_logreturns)
names(error_logreturns) <- c("rolling forecast", "static forecast")
plot(error_logreturns, col = c("black", "red"), lwd = 2,
     main = "Forecast error with eGARCH(1,1) model on Monthly Return", legend.loc = "topleft")
```


price forecast

```{r}
# simulate one path
garch_spec <- ugarchspec(mean.model = list(armaOrder = c(0,0), include.mean = TRUE), 
                         variance.model = list(model = "eGARCH", garchOrder = c(1,1)),
                         fixed.pars = as.list(coef(garch_fit))
                                               )

T <- 36
path_garch <- ugarchpath(garch_spec, m.sim = 3, n.sim = T, rseed=10)

str(path_garch@path$seriesSim)
plot.zoo(fitted(path_garch))
plot.zoo(sigma(path_garch))

fOrigin <- tail(index(train_monthlyR), 1)
fOriginPrice <- as.numeric(btc_monthly[fOrigin]$`BTC-USD.Close`)

p<-fOriginPrice*apply(fitted(path_garch),2,'cumsum') + fOriginPrice
matplot(p, type='l', lwd=3, main = "BTC Monthly Closing Price from eGARCH model")

d <- seq(as.Date(fOrigin+1),by='1 month',length=T) -1
p.xts <- xts(p, order.by=d)
plot(cbind("forecast"=p.xts,
           "actual"=window(btc_monthly,start=fOrigin)$`BTC-USD.Close`
           ), 
     lwd=3, main = "BTC Monthly Closing Price from eGARCH model", legend.loc = "topleft")

```




## Compare with Other Methods - TBC

```{r}

T <- nrow(diff1_log_btc_monthly)
T_trn <- round(0.8*T)
T_tst <- T - T_trn

train_monthlyR <- diff1_log_btc_monthly[1:T_trn,]
test_monthlyR <- diff1_log_btc_monthly[-c(1:T_trn),]

# plot
{ plot(diff1_log_btc_monthly, main = "Monthly Returns", lwd = 1.5)
  addEventLines(xts("training", index(diff1_log_btc_monthly[T_trn])), srt=90, pos=2, lwd = 2, col = "blue") }

var_constant <- var(train_monthlyR)  # or: mean(x_trn^2)
plot(cbind(sqrt(var_constant), train_monthlyR), col = c("red", "black"), lwd = c(2.5, 1.5),
     main = "Constant envelope")
```



## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
